---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  dev = 'jpeg'
)
```

# SoilProfileGraphs

<!-- badges: start -->
[![R-CMD-check](https://github.com/brownag/SoilProfileGraphs/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/brownag/SoilProfileGraphs/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of SoilProfileGraphs is to provide extensions for 'aqp' and 'ggplot2' for creation of soil profile-related graphics. The first focus is on 'calibrated' pit photographs with overplotting of soil property data.

## Installation

You can install the development version of SoilProfileGraphs like so:

``` r
# install.packages("remotes")
remotes::install_github("brownag/SoilProfileGraphs")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example-sueredo}
library(SoilProfileGraphs)
library(soilDB)

spc <- readRDS(system.file("extdata", "aecpedons.rds",
                           package = "SoilProfileGraphs"))[4, ]
lab <- soilDB::fetchLDM(spc$pedlabsampnum)

spg(
  lab,
  system.file("extdata", "sueredo.png",
              package = "SoilProfileGraphs"),
  prop = "sand_total",
  depth_min = -3,
  depth_max = 185,
  no_data_value = 76.5,
  prop_min = 65,
  prop_max = 95
)
```

```{r example-buttelake}
spc <- readRDS(system.file("extdata", "aecpedons.rds",
                           package = "SoilProfileGraphs"))[3, ]
lab <- soilDB::fetchLDM(spc$pedlabsampnum)

spg(
  lab,
  system.file("extdata", "buttelake.png",
              package = "SoilProfileGraphs"),
  prop = "sand_total",
  depth_min = -3,
  depth_max = 165,
  no_data_value = 76.5,
  prop_min = 50,
  prop_max = 100
)
```
